\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{circuitikz}
\usepackage{caption}
\usepackage{subcaption}
\hbadness=99999

\title{Investigation of the Wien's displacement law and the Stefan-Boltzmann law}
\author{Di Yan Xu, Rickie Li}
\date{\today}

\begin{document}

\maketitle

\newpage

\section{Introduction}
The purpose of this experiment is to test both the Wien's displacement law and
the Stefan-Boltzmann law. The Wien's displacement law is a law used to determine
the shift in temperature due to shift in wavelength or vice-versa. The theory
behind this is because for blackbodies, as the temperature increases, the peak
of the intensity of blackbody radiation shifts to lower wavelengths. The relation
behind the shift in temperature to wavelength can be seen as
\begin{align*}
    \lambda_{\max}T = 2.898\times10^{-3}m\cdot K
\end{align*}
Where $\lambda_{\max}$ is the wavelength at the peak, and $T$ is the absolute max
temperature of the emitting object.\\
The Stefan-Boltzmann law is the law used to determine the total intensity radiated
within all wavelength, mathmatically this is done by taking the area under the
graph of Planck's radiation law. Planck's radiation law is the following
\begin{align*}
    I(\lambda, T) &= \frac{2\pi c^2h}{\lambda^5}\frac{1}{e^{\frac{hc}{\lambda kT}} - 1}
\end{align*}
Where $h = 60626\times 10^{-34}J\cdot s$ is the Planck's constant, $k = 1.38
\times 10^{-23}m^2\cdot kg\cdot s^{-2}\cdot K^{-1}$ is the Boltzmann constant,
$T$ is the absolute temperature, and $\lambda$ is the wavelength.\\
To get the area under the curve for this, we would integrate over $\lambda$ to get
\begin{align*}
    \int_0^{\infty}I(\lambda, T) d\lambda &= \int_0^{\infty}
    \frac{2\pi c^2h}{\lambda^5}\frac{1}{e^{\frac{hc}{\lambda kT}} - 1}d\lambda\\
    &= 2\pi hc^2\int_0^{\infty}\frac{d\lambda}{\lambda^5}\frac{1}{e^{\frac{hc}{\lambda kT}} - 1}\\
    &= \sigma T^4
\end{align*}
Where $\sigma = 5.67 \times 10^{-8}W\cdot m^{-2}\cdot K^{-4}$ is the Stefan-Boltzmann
constant.

\newpage
\section{Methods}
Equipment used for the experiment are as follows
\begin{itemize}
    \item[-] A Prism
    \item[-] A Broad Spectrum Light Sensor
    \item[-] An Incandescent Light Bulb
    \item[-] A Signal Generator
    \item[-] A Collimating Lens
    \item[-] A Computer with the Blackbody Radiation Labview application
\end{itemize}
For the first part of this lab regarding Wien's Displacement Law, we turn on the 
signal generator and we place the Broad Spectrum Light Sensor at the stop with gain 
set to x10.  Then, when the room was dark, we turn acquisition on in the Blackbody
Radiation Labview application set to 30 degrees and some voltage and begin moving 
the Broad Spectrum Light Sensor until the acquisition automatically stops.  After that
we record the angle where the intensity appears to be at its max and the average voltage 
and current, then we export the data from the application into a text file.  We repeat 
this process starting from 4V and moving up by 1V up to 10V.  Every time we 
determine that there may be too much noise, we perform the procedure again with the same
voltage.

For the second part of this lab regarding the Stefan-Boltzmann Law, we repeat many of the 
steps in the previous part but with the application set to 80 degrees and instead of 
exporting the data, we placed two cursors at the ends of the main peak in the application 
and used the integrate button to record the area under the peak.  We also placed the two 
cursors outside of the main peak in order to integrate and determine the area under the 
noise which we recorded as the error.  We repeat this process starting from 4V and moving 
up by 1V up to 10V.

\newpage

\section{Analysis}
\subsubsection*{Calculate the experimental peak wavelength values $\lambda_{\exp}$}
We started by collecting data on the peaks with a set voltage $V = 5V$. Then
using the angle at which the curve hit it's peak, we compute the index of refraction
using the equation
\begin{align*}
    n = \sqrt{\bigg(\frac{2}{\sqrt{3}} \sin\theta + \frac{1}{2}\bigg)^2 + \frac{3}{4}}
\end{align*}
where $\theta = \theta_0 - \theta_{peak}$. We then converted all the index of
refraction values into wavelength values using the Cauchy equation for the relation
of index of refraction and wavelength.
\begin{align*}
    n(\lambda) &= \frac{A}{\lambda^2} + B\\
    \lambda &= \sqrt{\frac{A}{n - B}}
\end{align*}
Where the $A$ and $B$ values for the prism are $A = 13900$ and $B = 1.689$. 
Completing all the steps above, we have the calculated values of $\lambda_{\exp}$
in table 1.

\subsubsection*{Calculate temperature values $T$ using voltage and current}
We were able to calculate the temperature value using voltage and current with
the following equation
\begin{align*}
    T = 300K + \frac{\frac{V / I}{R_0} - 1}{\alpha_0}
\end{align*}
Using the above equation we calculated temperature values $T$ in Table 1.
\begin{center}
    \begin{tabular}{ c | c | c | c | c}
    $\theta_{peak}$ & Current ($A$) & Index & $\lambda_{\max} (nm)$ & Temperature($K$)\\
    \hline 
    23.314  &  0.429  &  1.701788  &  1042.53  &  2432.325 \\
    23.397  &  0.428  &  1.700997  &  1076.38  &  2437.826 \\
    23.667  &  0.429  &  1.698410  &  1215.33  &  2432.325 \\
    23.345  &  0.425  &  1.701493  &  1054.79  &  2454.486 \\
    23.538  &  0.428  &  1.699648  &  1142.51  &  2437.826 
    \end{tabular}
    \captionof{table}{Constant Voltage $V = 5V$}
\end{center}
\newpage
\subsubsection*{Use data from Wien's Law and calculate the average value of $T\times \lambda_{\exp}$.
How does it compare with Wien's Displacement Law}
Using data calculated from Table 1, we can calculate the average $\lambda_{\max}$
to be $\overline{\lambda_{\max}} = 1106 \pm 72 nm$, and the average $T$ is 
$\overline{T} = 2439 \pm 9 K$.
The error is calcualted to be the sample standard deviation. Multiplying these
values together we get
\begin{align*}
    \lambda * T &= 1.106\time 10^{-6}m * 2439 K\\
    &= 2.698 \times 10^{-3} m\cdot K
\end{align*}
We would have an error of
\begin{align*}
    \sigma &= 2.698 \times 10^{-3} \cdot \sqrt{\big(\frac{72}{1106}\big)^2 + 
    \big(\frac{9}{2439}\big)^2 }\\
    &= 1.759 \times 10^{-4}
\end{align*}
So our experimental Wien's law value is $2.698 \times 10^{-3} \pm 1.759 
\times 10^{-4} m\cdot K$

\subsubsection*{Use data from Stefan-Boltzmann Law and plot: Area vs. $T^4$. How 
well does your (qualitative) graph compares with the Stefan-Boltzmann Law?}
Using the data we collected, we calculated $T^4$, using the same equation that was 
previously used in the analysis, for each of our data points.  With the area and $T^4$
data, we can use curve fit to find a constant $a$ to be used in a model function given by,
\[f(x)=ax\] Where the temperature to the power of four, $x$, is the independent variable, 
and the area under the intensity curve, $f$, is the dependent variable.  With the data and 
the model function we can plot the following graph in figure 1,
%%%%%%%%%%%%%%%%%%insert graph%%%%%%%%%%%%%%%%%%%%%%%%%%
We can see in the graph that our data seems to follow the Stefan-Boltzmann Law equation in 
the sense that the area increases linearly with temperature to the power of four.  However,
it is possible that our data might not continue increasing linearly considering how our data
has $\chi^2_{red}=1.43$ which is greater than 1 and the last two data points do not have 
the model function value within the range of their y error.


\newpage
\subsubsection*{How did the colour of the bulb change with temperature? How did
the colour composition of the spectrum change with temperature? Considering the
peak wavelengths, why is a bulb's filament red at low temperatures and white at
high temperatures?}
To follow the Wien's displacement law, at lower temperatures there needs to be
longer wavelengths and vice-versa for shorter wavelength, a relation that can be
seen as 
\begin{align*}
    \lambda_{\max}\uparrow \implies T\downarrow \ \ \ \ \ \ \ \ \ 
    \lambda_{\max}\downarrow \implies T\uparrow
\end{align*}
Therefore this relation causes the colour of the bulb to change as the temperature
changes, in the spectrum of visible light the lower wavelengths appear has
all the colours of light thus appearing white, while for lower temperatures 
(higher wavelengths) would result in more red colours.

\subsubsection*{Last question all you}


\section{Conclusion}
When testing Wien's Displacement Law, the value for $\lambda_{max}T$ that we obtained 
using our data was $2.698 \times 10^{-3} \pm 1.759 \times 10^{-4} m\cdot K$ which contains 
the actual value of $\lambda_{max}T$ in Wien's Displacement Law, which is $2.898 \times 
10^{-3} m\cdot K$, within approximately 1.137 standard deviations.  When testing the 
Stefan-Boltzmann Law, we were able to plot the graph in figure 1 which shows that, at least 
for our data points considering the fairly high $\chi^2_{red}$ of 1.43, the area under 
the peak of the intensity vs angle graphs we obtained increases linearly with $T^4$ like 
the total intensity radiated within all wavelengths which is given by the Stefan-Boltzmann Law.


\end{document}